Factors affecting reliablity of state-space age-structured assessment models

### 2023-06-06 Project_0/paper/paper.Rmd
saving project_0 work

@@

@@

@@

@@

Do each of these by type of operating model (Naa, M, sel, q)
Convergence performance

@@

AIC performance

SR estimation? M estimation?

Bias, Mean Square error

  Certain basic parameters (stock-recruit pars, M, variance parameters)
  SSB, F, R

\clearpage 
## Numbers at age operating models

### Estimating models include alternative random effects options: NAA, M, sel, q
\clearpage

\begin{landscape}
\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on survival. Standard deviations (SD) are for log-normal distributed indices and logistic normal distributed age composition observations (fleet and indices). Fishing mortality changes after year 20 (of 40) for fishing histories where fishing mortality is not constant.}
{\footnotesize \input{naa_om_tab}}
\end{table}

\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on natural mortality. Standard deviations (SD) are for log-normal distributed indices and logistic normal distributed age composition observations (fleet and indices). Fishing mortality changes after year 20 (of 40) for fishing histories where fishing mortality is not constant. For AR1 process errors, $\sigma$ is defined for the marginal distribution of the processes.}
{\input{M_om_tab}}
\end{table}

\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on selectivity. Standard deviations (SD) are for log-normal distributed indices and logistic normal distributed age composition observations (fleet and indices). Fishing mortality changes after year 20 (of 40) for fishing histories where fishing mortality is not constant. For AR1 process errors, $\sigma$ is defined for the marginal distribution of the processes.}
{\input{Sel_om_tab}}
\end{table}

\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on catchability. Standard deviations (SD) are for log-normal distributed indices and logistic normal distributed age composition observations (fleet and indices). Fishing mortality changes after year 20 (of 40) for fishing histories where fishing mortality is not constant. For AR1 process errors, $\sigma$ is defined for the marginal distribution of the processes.}
{\input{q_om_tab}}
\end{table}
\end{landscape}

@@

@@

### Estimating models include NAA random effects and estimation assumes mean R or BH SR
\clearpage

\begin{table}
\caption{Operating models and estimation models all assume RE on recruitment only, estimating models assume mean recruitment or a B-H stock recruit relationship and M is fixed at the true value.}
{\input{rec_om_em_R_SR_MF_aic_table}}
\end{table}

\begin{table}
\caption{Operating models and estimation models all assume RE on recruitment only, estimating models assume mean recruitment or a B-H stock recruit relationship and M is estimated.}
{\input{rec_om_em_R_SR_ME_aic_table}}
\end{table}

\begin{table}
\caption{Operating models and estimation models all assume RE on all abundances at age, estimating models assume mean recruitment or a B-H stock recruit relationship and M is fixed at the true value.}
{\input{naa_om_em_R_SR_MF_aic_table}}
\end{table}

\begin{table}
\caption{Operating models and estimation models all assume RE on all abundances at age, estimating models assume mean recruitment or a B-H stock recruit relationship and M is estimated.}
{\input{naa_om_em_R_SR_ME_aic_table}}
\end{table}
\clearpage

\begin{figure}
\caption{Predicted probability of AIC being better for BH model.}\label{glm_res_NAA_re}
\begin{center}
\includegraphics[width = \textwidth]{pred_SR_best_NAA_oms.png}
\end{center}
\end{figure}

## M operating models

### Estimating models include NAA random effects and estimation assumes mean R or BH SR

\begin{table}
\caption{M random effects operating models.}
{\input{M_om_em_R_BH_aic_table}}
\end{table}
\clearpage

>>>>

\begin{landscape}
\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on survival. Standard deviations (SD) are for log-normal distributed indices and logistic normal distributed age composition observations (fleet and indices). Fishing mortality changes after year 20 (of 40) for fishing histories where fishing mortality is not constant.}
{\footnotesize \input{naa_om_tab}}
\end{table}
\end{landscape}

@@

\begin{landscape}
\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on natural mortality. Standard deviations (SD) are for log-normal distributed indices and logistic normal distributed age composition observations (fleet and indices). Fishing mortality changes after year 20 (of 40) for fishing histories where fishing mortality is not constant. For AR1 process errors, $\sigma$ is defined for the marginal distribution of the processes.}
{\input{M_om_tab}}
\end{table}
\end{landscape}

@@

\begin{landscape}
\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on selectivity. Standard deviations (SD) are for log-normal distributed indices and logistic normal distributed age composition observations (fleet and indices). Fishing mortality changes after year 20 (of 40) for fishing histories where fishing mortality is not constant. For AR1 process errors, $\sigma$ is defined for the marginal distribution of the processes.}
{\input{Sel_om_tab}}
\end{table}
\end{landscape}

@@

\begin{landscape}
\begin{table}
\caption{Distinguishing characteristics of the operating models with random effects on catchability. Standard deviations (SD) are for log-normal distributed indices and logistic normal distributed age composition observations (fleet and indices). Fishing mortality changes after year 20 (of 40) for fishing histories where fishing mortality is not constant. For AR1 process errors, $\sigma$ is defined for the marginal distribution of the processes.}
{\input{q_om_tab}}
\end{table}
\end{landscape}

@@

Do each of these by type of operating model (Naa, M, sel, q)

## Convergence performance

@@

### R, R+S operating models

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structures R and R+S. vertical lines represent 95\% confidence intervals. All estimating models estimate mean recruitment rather than a stock-recruit relationship and and M is fixed at the true value.}\label{naa_om_em_R_MF_convergence}
\begin{center}
\includegraphics[width = \textwidth]{naa_om_p_convergence_meanR_M_fixed.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structures R and R+S. vertical lines represent 95\% confidence intervals. All estimating models estimate mean recruitment rather than a stock-recruit relationship and and M is estimated.}\label{naa_om_em_R_ME_convergence}
\begin{center}
\includegraphics[width = \textwidth]{naa_om_p_convergence_meanR_M_estimated.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structures R and R+S. vertical lines represent 95\% confidence intervals. All estimating models estimate a Beverton-Holt stock-recruit relationship and and M is fixed at the true value.}\label{naa_om_em_BH_MF_convergence}
\begin{center}
\includegraphics[width = \textwidth]{naa_om_p_convergence_BH_M_fixed.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structures R and R+S. vertical lines represent 95\% confidence intervals. All estimating models estimate a Beverton-Holt stock-recruit relationship and and M is estimated.}\label{naa_om_em_BH_ME_convergence}
\begin{center}
\includegraphics[width = \textwidth]{naa_om_p_convergence_BH_M_estimated.png}
\end{center}
\end{figure}
\end{landscape}

### R+M operating models

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+M. vertical lines represent 95\% confidence intervals. All estimating models estimate mean recruitment rather than a stock-recruit relationship and and M is fixed at the true value.}\label{M_om_em_R_MF_convergence}
\begin{center}
\includegraphics[width = \textwidth]{M_om_p_convergence_meanR_M_fixed.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+M. vertical lines represent 95\% confidence intervals. All estimating models estimate mean recruitment rather than a stock-recruit relationship and and M is estimated.}\label{M_om_em_R_ME_convergence}
\begin{center}
\includegraphics[width = \textwidth]{M_om_p_convergence_meanR_M_estimated.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+M. vertical lines represent 95\% confidence intervals. All estimating models estimate a Beverton-Holt stock-recruit relationship and and M is fixed at the true value.}\label{M_om_em_BH_MF_convergence}
\begin{center}
\includegraphics[width = \textwidth]{M_om_p_convergence_BH_M_fixed.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+M. vertical lines represent 95\% confidence intervals. All estimating models estimate a Beverton-Holt stock-recruit relationship and and M is estimated.}\label{M_om_em_BH_ME_convergence}
\begin{center}
\includegraphics[width = \textwidth]{M_om_p_convergence_BH_M_estimated.png}
\end{center}
\end{figure}
\end{landscape}

### R+Sel operating models

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+Sel. vertical lines represent 95\% confidence intervals. All estimating models estimate mean recruitment rather than a stock-recruit relationship and and M is fixed at the true value.}\label{Sel_om_em_R_MF_convergence}
\begin{center}
\includegraphics[width = \textwidth]{Sel_om_p_convergence_meanR_M_fixed.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+Sel. vertical lines represent 95\% confidence intervals. All estimating models estimate mean recruitment rather than a stock-recruit relationship and and M is estimated.}\label{Sel_om_em_R_ME_convergence}
\begin{center}
\includegraphics[width = \textwidth]{Sel_om_p_convergence_meanR_M_estimated.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+Sel. vertical lines represent 95\% confidence intervals. All estimating models estimate a Beverton-Holt stock-recruit relationship and and M is fixed at the true value.}\label{Sel_om_em_BH_MF_convergence}
\begin{center}
\includegraphics[width = \textwidth]{Sel_om_p_convergence_BH_M_fixed.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+Sel. vertical lines represent 95\% confidence intervals. All estimating models estimate a Beverton-Holt stock-recruit relationship and and M is estimated.}\label{Sel_om_em_BH_ME_convergence}
\begin{center}
\includegraphics[width = \textwidth]{Sel_om_p_convergence_BH_M_estimated.png}
\end{center}
\end{figure}
\end{landscape}

### R+q operating models

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+q. vertical lines represent 95\% confidence intervals. All estimating models estimate mean recruitment rather than a stock-recruit relationship and and M is fixed at the true value.}\label{q_om_em_R_MF_convergence}
\begin{center}
\includegraphics[width = \textwidth]{q_om_p_convergence_meanR_M_fixed.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+q. vertical lines represent 95\% confidence intervals. All estimating models estimate mean recruitment rather than a stock-recruit relationship and and M is estimated.}\label{q_om_em_R_ME_convergence}
\begin{center}
\includegraphics[width = \textwidth]{q_om_p_convergence_meanR_M_estimated.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+q. vertical lines represent 95\% confidence intervals. All estimating models estimate a Beverton-Holt stock-recruit relationship and and M is fixed at the true value.}\label{q_om_em_BH_MF_convergence}
\begin{center}
\includegraphics[width = \textwidth]{q_om_p_convergence_BH_M_fixed.png}
\end{center}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\caption{Probability of each type of convergence of estimating models with alternative process error assumptions for operating models that have process error structure R+q. vertical lines represent 95\% confidence intervals. All estimating models estimate a Beverton-Holt stock-recruit relationship and and M is estimated.}\label{q_om_em_BH_ME_convergence}
\begin{center}
\includegraphics[width = \textwidth]{q_om_p_convergence_BH_M_estimated.png}
\end{center}
\end{figure}
\end{landscape}

## AIC performance for process error structure
\clearpage 
### Numbers at age operating models

## Estimating models include alternative random effects options: NAA, M, sel, q
\clearpage

@@

\clearpage 
## AIC performance for stock-recruit relationship

### R, R+S operating models

\begin{table}
\caption{Operating models and estimation models all assume matching R or R+S process error structure, estimating models assume mean recruitment or a B-H stock recruit relationship and M is either fixed at the true value or estimated.}
{\input{naa_om_em_R_BH_aic_table}}
\end{table}

\begin{figure}
\caption{Predicted probability of AIC preferring BH model as a function of the variation of population SSB. Operating and estimating models have matching R or R+S process error structures. Estimating models assume mean M is fixed at the true value.}\label{naa_om_MF_BH_glm_AIC_plots}
\begin{center}
\includegraphics[width = \textwidth]{naa_om_MF_pred_BH_best.png}
\end{center}
\end{figure}

\begin{figure}
\caption{Predicted probability of AIC preferring BH model as a function of the variation of population SSB. Estimating models allow estimation of mean M.}\label{naa_om_ME_BH_glm_AIC_plots}
\begin{center}
\includegraphics[width = \textwidth]{naa_om_ME_pred_BH_best.png}
\end{center}
\end{figure}

### R+M operating models

\begin{table}
\caption{Operating models and estimation models all assume matching R+M process error structure, estimating models assume mean recruitment or a B-H stock recruit relationship and M is either fixed at the true value or estimated.}
{\input{M_om_em_R_BH_aic_table}}
\end{table}

\begin{figure}
\caption{Predicted probability of AIC preferring BH model as a function of the variation of population SSB. Operating and estimating models have matching R+M process error structures. Estimating models assume mean M is fixed at the true value.}\label{M_om_MF_BH_glm_AIC_plots}
\begin{center}
\includegraphics[width = \textwidth]{M_om_MF_pred_BH_best.png}
\end{center}
\end{figure}

\begin{figure}
\caption{Predicted probability of AIC preferring BH model as a function of the variation of population SSB. Operating and estimating models have matching R+M process error structures. Estimating models allow estimation of mean M.}\label{M_om_ME_BH_glm_AIC_plots}
\begin{center}
\includegraphics[width = \textwidth]{M_om_ME_pred_BH_best.png}
\end{center}
\end{figure}

### R+Sel operating models

\begin{table}
\caption{Operating models and estimation models all assume matching R+Sel process error structure, estimating models assume mean recruitment or a B-H stock recruit relationship and M is either fixed at the true value or estimated.}
{\input{Sel_om_em_R_BH_aic_table}}
\end{table}

\begin{figure}
\caption{Predicted probability of AIC preferring BH model as a function of the variation of population SSB. Operating and estimating models have matching R+Sel process error structures. Estimating models assume mean M is fixed at the true value.}\label{Sel_om_MF_BH_glm_AIC_plots}
\begin{center}
\includegraphics[width = \textwidth]{Sel_om_MF_pred_BH_best.png}
\end{center}
\end{figure}

\begin{figure}
\caption{Predicted probability of AIC preferring BH model as a function of the variation of population SSB. Operating and estimating models have matching R+Sel process error structures. Estimating models allow estimation of mean M.}\label{Sel_om_ME_BH_glm_AIC_plots}
\begin{center}
\includegraphics[width = \textwidth]{Sel_om_ME_pred_BH_best.png}
\end{center}
\end{figure}

### R+q operating models

\begin{table}
\caption{Operating models and estimation models all assume matching R+q process error structure, estimating models assume mean recruitment or a B-H stock recruit relationship and M is either fixed at the true value or estimated.}
{\input{q_om_em_R_BH_aic_table}}
\end{table}

\begin{figure}
\caption{Predicted probability of AIC preferring BH model as a function of the variation of population SSB. Operating and estimating models have matching R+q process error structures. Estimating models assume mean M is fixed at the true value.}\label{q_om_MF_BH_glm_AIC_plots}
\begin{center}
\includegraphics[width = \textwidth]{q_om_MF_pred_BH_best.png}
\end{center}
\end{figure}

\begin{figure}
\caption{Predicted probability of AIC preferring BH model as a function of the variation of population SSB. Operating and estimating models have matching R+q process error structures. Estimating models allow estimation of mean M.}\label{q_om_ME_BH_glm_AIC_plots}
\begin{center}
\includegraphics[width = \textwidth]{q_om_ME_pred_BH_best.png}
\end{center}
\end{figure}

\clearpage 
## Bias, Mean Square error

  Certain basic parameters (stock-recruit pars, M, variance parameters)
  SSB, F, R, BRPs

@@
